Highlights

### 2017-02-12 reports/highlights.tex
Added paper's highlights for Pattern Recognition

\title{Author Biography}

@@

\begin{itemize}
  \item John A. Ramey is Principal Data Scientist at Novi Labs, an Austin-based startup focused on optimizing oil and gas drilling and completion designs. He graduated in 2012 with a Ph.D. in Statistics from Baylor University and completed a postdoc at Fred Hutchinson Cancer Research Center.
  \item Caleb K. Stein earned BA from the University of Arkansas, earned an MS in Statistics and currently enrolled in PhD program at Baylor University. Stein's publications include investigations of gene expression and mutation calls from Multiple Myeloma patient data, batch effect correction, and clinical outcome analyses.
  \item Phil D. Young is Clinical Assistant Professor in the Department of Information Systems at Baylor University. He graduated with a Ph.D. in Statistics from Baylor University in 2009. His fields of interest include statistical pattern recognition and classification.
  \item Dean M. Young is Professor of Statistics at Baylor University. His research interests include pattern recognition, multivariate analysis, and computational statistics.
\end{itemize}

>>>>

\title{Highlights}

@@

\begin{itemize}
  \item We present an efficient classifier designed for small-sample, high-dimensional data.
  \item Interpretable alternative to Friedman's Regularized Discriminant Analysis.
  \item HDRDA's matrix operations are linear in the number of features.
  \item Timing comparisons show our classifier is substantially faster than Friedman's RDA.
  \item Often superior to sparse and regularized classifiers in classification accuracy.
\end{itemize}
